### 2015-03-26 paper.tex
Added some more info to paper and started working on the presentation

The GNU General Public License License v2 or GPLv2 is the most commonly used free software license today. It is used in various major projects including; Linux, \textbf{Add more projects}.

@@

@@

The GNU Affero General Public License was designed to close a perceived loophole in the original GPL.

@@

\subsubsection{APSL}
\subsubsection{CeCILL}
\subsubsection{MPL}
\subsubsection{IPL}

\section{Limited Copyleft}

\subsection{CDDL}

>>>>

The GNU General Public License License v2 or GPLv2 is the most commonly used free software license today. It is used in various open source projects, the most major one being Linux.

@@

\textbf{CONTINUE THIS, there is a lot more information to cover in this topic}

@@

The GNU Affero General Public License was designed to close a perceived application service provider loophole in the original GPL. This additional provision requires that  that the complete source code be made available to any network user of the AGPL-licensed work.

@@

\subsubsection{APSL}

The Apple Public Source License was the original license under which Apple's Darwin operating system was created. While APSL is fully copyleft and the FSF supports the license, they do no longer recommend it since it allows linking with entirely proprietary files. This license was essential in the first stages of Apple, however today most of the software released by the company now use the Apache license.
